%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Template
% Version 1.0 (28/1/19)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended
\usepackage{enumitem}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.45\textwidth} % 45% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% If your name is very short, use just one of the lines below
	% If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{Yao Xiao}}}} % First name	
	\vspace{6pt}
	
	{\huge Staff Software Engineer} % Career or current job title
\end{minipage}
\begin{minipage}[t]{0.30\textwidth} % 27.5% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{Phone}{12}{(650)-304-5470}\\
	\icon{At}{12}{\href{mailto:xarvey1111@gmail.com}{xarvey1111@gmail.com}}\\	
	\icon{Linkedin}{12}{\href{https://www.linkedin.com/in/yao-xiao-87341079/}{linkedin.com/in/xiaoyao-1111}}\\

\end{minipage}
\begin{minipage}[t]{0.30\textwidth} % 27.5% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{Globe}{12}{\href{https://xarvey.github.io}{xarvey.github.io}}\\
	\icon{Github}{12}{\href{https://github.com/xarvey}{github.com/xarvey}}\\
\end{minipage}

\vspace{0.5cm}

%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------



%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Experience}

\begin{entrylist}
	\entry
		{2017/8 -- Current}
		{Staff Software Engineer/Tech Lead}
		{Meta Platforms(fka. Facebook), Inc.\\\footnotesize{Menlo Park, CA/Sunnyvale, CA/New York, NY}} 
		{
			\begin{itemize}[leftmargin=-0.0125in]
				\item Led a team of \textbf{5} engineers to architect and execute a multi-phase integrity enforcement platform strategy, focusing on improving system reliability, governance, infrastructure modernization, and integration of large language models (\textbf{LLMs}).
				\item Developed and executed platform long-term strategy aligned with product vision, scoping \textbf{10+} senior engineer projects from scratch.
				\item Assumed interim engineering management during organizational transitions, maintaining team velocity, morale, and seamless project delivery.
				\item Directed migration of \textbf{7+} legacy systems (in PHP, Haskell and Python) into a unified, scalable platform, boosting developer productivity and reducing operational overhead.
				\item Maintained and enhanced a global work distribution tool, supporting \textbf{180,000+} content reviewers worldwide by troubleshooting complex technical issues and optimizing workflow processes.
				\item Spearheaded migration of job-reviewer matching infrastructure to a push-based system using a bipartite matching algorithm, increasing matching efficiency by \textbf{10\%} and significantly reducing reviewer workload.
				\item Built a developer and code-generation platform that enabled \textbf{50+} product launches and supported \textbf{75 million} weekly reviewer jobs, ensuring scalability and maintainability.
				\item Developed a self-service management tool enabling approximately \textbf{200} non-engineer employees to manage content review pipeline settings, reducing engineering support tickets through self-service.
				\item Redesigned the content reviewers’ front page by developing a data pipeline that aggregates and displays key performance insights, enhancing reviewer visibility and productivity.
				\item Conducted \textbf{200+} technical interviews, reviewed engineering design docs, mentored junior and senior engineers and interns, and led onboarding to accelerate team growth and capability.
			\end{itemize}
		}
	\entry
		{2016/5 -- 2016/8}
		{Software Engineer Intern}
		{Bloomberg L.P. \\\footnotesize{New York, NY}}
		{
			\begin{itemize}[leftmargin=-0.0125in]
		\item Developed a rule engine in Scala using Apache Spark to support a new product, and integrated it with existing APIs to process billions of data points per day.
	 	\end{itemize}
		}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.4\textwidth} % 50% of the page for the skills bar chart
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	\cvsect{Skills}

	\begin{barchart}{4}
		\baritem{Hack/PHP}{90}
		\baritem{React/Relay/GraphQL/NextJS/NodeJS/JavaScript}{80}
		\baritem{Airflow/SQL}{70}
		\baritem{Git/Mercurial}{70}
		\baritem{Python}{60}
		\baritem{\LaTeX}{30}
		\baritem{Haskell}{20}
	\end{barchart}
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Languages}
	
	\textbf{English} - proficient\\
	\textbf{Chinese} - native\\
	\textbf{Spanish} - rudimentary

	\cvsect{Side Project}
	\\
	Created an online murder mystery game using NodeJS, GraphQL, React, and MongoDB during COVID-19. Played over 20 hours with friends
\end{minipage}
\hfill

\cvsect{Education}

\begin{entrylist}
	\entry
		{2013 -- 2017}
		{Bachelor of Science in Computer Science with a Minor in Math}
		{Purdue University \\\footnotesize{West Lafayette, IN}}
		{Overall GPA: 3.7/4.0}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------

\end{document}
